%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
    
% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

%
% These commands are for a JOURNAL article.
%\setcopyright{acmcopyright}
%\acmJournal{TOG}
%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
%\acmDOI{10.1145/1122445.1122456}

%
% Submission ID. 
% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

%
% end of the preamble, start of the body of the document source.
\begin{document}

%
% The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
\title{Grand Challenge: A Real-Time Multi-label Classifier for High-Speed Streaming Data}

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.



\author{Sambasiva Rao Gangineni}
\affiliation{%
  \institution{Boston University}  
}
\email{samba693@bu.edu}

\author{Harshad Reddy Nalla}
\affiliation{%
	\institution{Boston University}  
}
\email{harshad@bu.edu}

\author{Dimitrije Jankov}
\affiliation{%
	\institution{Rice University}  
}
\email{dimitrijejankov@gmail.com}

\author{Saeed Fathollahzadeh}
\affiliation{%
	\institution{Iran University of Science and Technology}  
}
\email{fathollahzadeh@comp.iust.ac.ir}

\author{Kia Teymourian}
\affiliation{%
  \institution{Boston University}
 }
\email{kiat@bu.edu}



%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
\renewcommand{\shortauthors}{Kia Teymourian, et al.}

%
% The abstract is a short summary of the work to be presented in the article.
\begin{abstract}
The winners of the challenge are announced during the conference. The 2019 DEBS Grand Challenge focuses on the application of machine learning to LiDAR data. The goal of the challenge is to perform classification of objects in different scenes surveyed by the LiDAR. The applications of LIDAR and object detection go well beyond autonomous vehicles and are suitable for use in agriculture, waterway maintenance and flood prevention, and construction.

In this paper, we describe our implementation for ACM DEBS 2019 Grand Challenge for a high-speed online neural network classifier that is highly customized to classify objects from streaming data in real-time.
\end{abstract}

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information Systems~Machine Learning}
\ccsdesc[300]{Information Systems~Data Stream}

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{neural networks, multi-label classification, data stream processing}



%
% This command processes the author and affiliation and title information and builds
% the first part of the formatted document.
\maketitle

\section{Introduction}
Many real-world applications include multi-lable data and require real-time high-speed multi-lable classification. In most application, it is crucial to proactively react based on classification results. For example, in autonomous car application it is important to detect surrounding cars and pedestrians in real-time to send reaction signals. 

\input{relatedWork}

\input{data}

\input{architecture}

\input{evaluation}

\input{conclusion}


\bibliographystyle{ACM-Reference-Format}
\bibliography{refrences}




\end{document}
